### 2018-10-04 paper/paper.tex
def LTS

Introduce abbreviations:
\begin{itemize}
\item Lead Time Syndrome (\LTS{})
\item Work-in-process (\WIP{})
\end{itemize}

@@

\begin{definition}
  We define the \emph{time span} $\ts(p)$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \ts(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff todo}} \tcom
  \end{align*}
  where $\zs$ can be used to scale the confidence interval being considered.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate

@@

The reduce the impact of outliers we average the actual releases over $k$ values.

>>>>

Introduce abbreviations:
\begin{itemize}
\item Lead Time Syndrome (\LTS{})
\item Work-in-process (\WIP{})\\
\end{itemize}

Definition LTS~\citep{selccuk2013adaptive}: dynamic quoting of lead times $\rightarrow$ lumpy releases $\rightarrow$ larger
WIP $\rightarrow$ longer lead times $\rightarrow$ more releases\\

@@

\begin{definition}
  We define the \emph{time span} $\ts(p)$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \ts(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff todo}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval being considered.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate

@@

The reduce the impact of outliers we average the actual releases over $ts(p)$ values.
